\begin{recipe}{Challah}{1 loaf}{}
\freeform 
\ing[2 1/4]{tsp}{yeast}
\ing[1]{cup}{warm water}
Activate the yeast in warm water and let stand for about 5-10 minutes or until bubblty.
\ing[3 1/2]{cups}{flour}
\ing[1/2 to 3/4]{cup}{sugar}
\ing[1]{tsp}{salt}
Add the flour, sugar and salt on top of the water layer to separate the dry and the wet ingredients.
\ing[2]{T}{butter}
\ing[2]{}{eggs}
\ing[]{}{Melt the butter and add one egge to it. Whisk together and add on top of the dry ingredients. Blend all the ingredients together in a bowl and knead for about 10 minutes to form a stiff dough. Cover the dough and let rise for 2-4 hours, or until doubled in size. Punch the air out of the dough and cut into 3 or 6 pieces for braiding. Braid the challah and then place on a baking sheet with corn meal on the bottom and allow to rise (covered) for another 2-4 hours or until it has grown to desired size. Brush the second egg (whisked) on top of the bread and then cook at 350F for about 30 minutes, or until golden brown on top.}
Melt the butter and add one egge to it. Whisk together and add on top of the dry ingredients. Blend all the ingredients together in a bowl and knead for about 10 minutes to form a stiff dough. Cover the dough and let rise for 2-4 hours, or until doubled in size. Punch the air out of the dough and cut into 3 or 6 pieces for braiding. Braid the challah and then place on a baking sheet with corn meal on the bottom and allow to rise (covered) for another 2-4 hours or until it has grown to desired size. Brush the second egg (whisked) on top of the bread and then cook at 350F for about 30 minutes, or until golden brown on top.
\end{recipe}
